---
title: "Take Home Assignment 4"
author: "Alex Toups"
date: "November 21, 2019"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#---------------------------------------------------------------------------------------------------#                #     Take Home Assignment 4                                                                        #
#       A. Toups November 21, 2019  atoups@tulane.edu                                               #
#                                                                                                   #
#   Description: Script will answer the questions to Take Home Assignment 4.                        #                #                                                                                                   #
#                                                                                                   #
#   Dependencies: Script requires use of the tidyverse and Hmisc packages but only for              #
#   illustrative purposes. All other function calls are contained in base R installs as             #
#   of version 3.5.3                                                                                #
#---------------------------------------------------------------------------------------------------#

library(tidyverse)
library(Hmisc)

ghana <- read_csv("ghana_bednet.csv")

```

```{r docinfo, echo = FALSE}

date()
sessionInfo()
```

#Question 1 & 2

```{r}
dim(ghana)
```

#There are 26,342 observations and 8 variables.

#Question 3

```{r}
typeof(ghana)
str(ghana)


ghana$sex[ghana$sex == "F"] <- 1
ghana$sex[ghana$sex == "."] <- NA


describe (ghana$sex) #edit accordinly
```

#The proportion of males represented in the population is .505.

#Question 4

```{r}

describe(ghana$follyr)

fu <- ghana %>%
        filter(sex == 1 & bednet == 1) %>%
        summarise(fu = sum(follyr, na.rm = TRUE))

sum(fu)
```

# The total number of person years of follow up is 8395.184 for females in the intervention.

#Question 5

```{r}

cluster <- filter(ghana, cluster == 52)

prop <- filter(ghana, cluster == 52, outcome == 1)

dim(cluster)
dim(prop)
  9/370
  
# THis is correct answer but a poor approach, you dont want to hard code results like this, better to use the filter as you did, then summarize the resulting dataset.... 

```

#The proportion of all children in cluster 52 who died during follow up is .0243.
  
#Question 6

```{r}
mean(ghana$agemn)
sd(ghana$agemn)
```
  
#The mean age is 25.29, and the standard deviation of age is 18.02.

#Question 7 

```{r}
mortality <- ghana %>%
  group_by(bednet)%>%
  summarise(mortality = sum(outcome)/sum(follyr, na.rm = TRUE))

mortality
```

#The mortality rate in the control arm is .0280, and the mortality rate in the intervention arm is .0235.

#Question 8

```{r}
ghana %>% group_by(bednet, cluster) %>%
    summarise(prop_dead = sum(ghana$outcome)/n()) %>%
    ggplot(aes(x = cluster, y = prop_dead, fill = as.factor(bednet))) +
    geom_bar(stat = "identity")
```

#Question 9

```{r}
fit <- glm(outcome ~ bednet, binomial(link = "logit"), data = ghana)

summary(fit)
```

#Question 10

```{r}
OR <- exp(-.17937)
OR
```

#The intervention cluster is associated with a lower probability of a child dying throughout follow up. The odds ratio is 0.84.

#The coefficient for this conclusion is -0.17937 (p = .01).
