---
title: "Exam 3"
author: "Alex Toups"
date: "12/15/2019"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#---------------------------------------------------------------------------------------------------#                      Exam 3                                                                                            #
#    A. Toups November 21, 2019  atoups@tulane.edu                                                  #
#                                                                                                   #
#   Description: Script will answer the questions to Exam 3.                                        #                                                             
#                                                                                                   #
#   Dependencies: Script requires use of the dplyr, plyr, and ggplot2 packages but only for                   #
#   illustrative purposes. All other function calls are contained in base R installs as             #
#   of version 3.5.3                                                                                #
#---------------------------------------------------------------------------------------------------#

library(dplyr)
library(plyr)
library(ggplot2)

```

```{r docinfo, echo = FALSE}

date()
sessionInfo()
```

#Question 1 & 2

```{r}
nola_crime <- read.csv("C:/Users/Alex/Documents/Tulane/2019-2020/2019/Stats Packages/Exam 3/nola_crime_2018.csv")

dim(nola_crime)
```
#There are 9,970 observations and 24 variables in the dataset.

#Question 3

```{r}
unique <- nola_crime %>%
  arrange(Item_Number) %>%
  distinct(Item_Number, .keep_all = TRUE) %>%
  ungroup()
```

#There are 9,384 unique item numbers.

#Question 4

```{r}

Irish <- filter(unique, GNOCDC_LAB == "IRISH CHANNEL" & Signal_Description == "AGGRAVATED ASSAULT")
dim(Irish)
```
#There is 1 "aggravated" crime in the Irish Channel Neighborhood. 

#Question 5
```{r}

neighborhood <- data.frame(table(unique$GNOCDC_LAB))
neighborhood[rev(order(neighborhood$Freq)),]
```
#French Quarter and Little Woods have the largest number of crime reports. 

#Question 6
```{r}
neighborhood_prop <- neighborhood[, -1]/1000
```
#Question 7
```{r}
unique_pop <- nola_crime %>%
  arrange(pop) %>%
  distinct(pop, .keep_all = TRUE) %>%
  ungroup()


max(unique$pop, unique$GNOCDC_LAB, na.rm = TRUE)

```

#The largest neighborhood by total population is Little Woods with a population of 44,947. 


#Question 8
```{r}
neighborhood[rev(order(neighborhood$Freq)),]

unique_pop[2, 23:24]
```
#The neighborhood with the lowest rate of crime is Florida Development with a population of 4,976. 


#Question 9

#Question 10

#Question 11
```{r}
mode(unique$Signal_Description)

mode(unique$Charge_Description)
```
#The most common cause for a police report to be filed is domestic disturbance, and the most common charge that is filed is theft. 

#Question 12

#Question 13

#Question 14

```{r}
low <- count(unique, vars=c("GNOCDC_LAB","pop"))
    arrange(low, low$freq)
```
#Lakewood has a population of 13,989 but a very low reporting rate so this hypothesis might be true of this neighborhood. 

#Question 15
```{r}
d <- rpois(n = 10000, lambda = 4.7)

data <- data.frame(d = d, 
                   col = ifelse(d < 5, "red", "blue"))



ggplot(data, aes(x = d, fill = col)) +
  geom_histogram(bins = 14, color = "black")

```
#Question 16
```{r}
iris %>% group_by(Species) %>%
  summarize(mean.sepal.length = mean(Sepal.Length))
```
#The mean Sepal length is 5.843. 

#Question 17
```{r}
reg1 <- lm(mpg~disp,data=mtcars) 
summary(reg1)

with(mtcars,plot(disp, mpg))
abline(reg1)

```

#Question 18
```{r}
data <- c(-4.89, -1.93, -1.11, 3.94, 0.46, -3.85, -0.20, 6.04,
9.36, 7.26, 4.88, 13.45, -2.93, 6.39, -16.22, -3.24, 6.86, 11.87, 1.81, -2.54)

pop_sd <- sd(data)*sqrt((length(data)-1)/(length(data)))
pop_mean <- mean(data)

z <- (data - pop_mean) / pop_sd

z
```
